Quick, Draw! Image Classification

### 2018-12-08 report/draft.tex
review 3.3.2

We found that imbalanced class prediction can be improved by adding more
data to the minority class. As shown in Figure \ref{fig:h4Results},

shows us that

a
decrease in class imbalance leads to an increase in prediction accuracy
for the minority class. These predictions were based on 20,000 total
samples which were previously unseen.

>>>>

We are able to confirm that adding data to the minority class to reduce
class imbalance increases prediction accuracy. Figure \ref{fig:h4Results}
shows results that support this assertion by gradually decreasing the class
imbalance by increasing the number of samples within the minority class.
Minority class accuracy ranged from 43\% with a 1:500 class imbalance to
98\% with a 1:1 class imbalance.These predictions were based on 20,000 total
samples which were previously unseen. The neural network models we
tested tended to generalize well on the most important weights, while
attempting to classify only the minority categories.
